---
title: 'No-match data exploration'
author: "Saurabh Khanna"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: 3
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE, fig.retina = 4)
knitr::opts_chunk$set(fig.pos = 'H')
```

```{r}
# Libraries
pacman::p_load(tidyverse, readxl, janitor, lubridate, extrafont)

# Parameters
df_nomatch <- read_xlsx(here::here("data", "merge/lirs_postresponses_nomatch_all_september.xlsx"))
df_baseline <- read_csv(here::here("data", "Rapid_response_baseline_cleaned_all_consent.csv"))
df_whatsapp_twilio <- read_xlsx(here::here("data/merge", "whatsapp_twilio.xlsx"))
df_sms_twilio <- read_xlsx(here::here("data/merge", "sms_twilio.xlsx"))

df_twilio <- 
  bind_rows(
    df_whatsapp_twilio %>% select(study_ID, number = whatsAppNumber_final, lang = languageFollowUps), 
    df_sms_twilio %>% select(study_ID, number = smsNumber_final, lang = languageFollowUps),
    .id = "medium"
  ) %>% 
  mutate(
    medium = recode(medium, `1` = "WhatsApp", `2` = "SMS", .default = NA_character_),
  ) %>% 
  distinct(study_ID, .keep_all = TRUE) %>% 
  distinct(number, .keep_all = TRUE)

failed_nos <- 
  read_csv(here::here("data", "merge/failed_messages.csv")) %>% 
  mutate(number_from = parse_number(`To Number`) %>% as.character()) %>% 
  distinct(number_from) %>% 
  unlist()

rm(df_whatsapp_twilio, df_sms_twilio)
```


```{r}
df_nomatch <-
  df_nomatch %>%
  mutate(date = as_datetime(date)) %>% 
  mutate_at(vars(starts_with("n")), parse_number) %>% 
  arrange(number, desc(date)) %>% 
  distinct(number, .keep_all = TRUE) %>% 
  mutate(number = as.character(number)) %>% 
  left_join(df_twilio, by = "number") %>% 
  left_join(df_baseline %>% select(-starts_with("q")), by = "study_ID") %>% 
  filter(!(number %in% failed_nos)) %>% 
  mutate(
    lang = if_else(lang %in% c("Don't know", "Refused"), NA_character_, lang),
    lang_match = 
      case_when(
        lang == "Arabic" & Arabic %in% c("NATIVE", "R", "RW", "W", "R NATIVE", "RW NATIVE") ~ "Match",
        lang == "Dari/Farsi" & Farsi %in% c("NATIVE", "R", "RW", "W", "R NATIVE", "RW NATIVE") ~ "Match",
        lang == "Dari/Farsi" & Dari %in% c("NATIVE", "R", "RW", "W", "R NATIVE", "RW NATIVE") ~ "Match",
        lang == "English" & English %in% c("NATIVE", "R", "RW", "W", "R NATIVE", "RW NATIVE") ~ "Match",
        lang == "Farsi" & Farsi %in% c("NATIVE", "R", "RW", "W", "R NATIVE", "RW NATIVE") ~ "Match",
        lang == "Farsi" & Dari %in% c("NATIVE", "R", "RW", "W", "R NATIVE", "RW NATIVE") ~ "Match",
        lang == "French" & French %in% c("NATIVE", "R", "RW", "W", "R NATIVE", "RW NATIVE") ~ "Match",
        lang == "Russian" & Russian %in% c("NATIVE", "R", "RW", "W", "R NATIVE", "RW NATIVE") ~ "Match",
        lang == "Spanish" & Spanish %in% c("NATIVE", "R", "RW", "W", "R NATIVE", "RW NATIVE") ~ "Match",
        lang == "Swahili" & Swahili %in% c("NATIVE", "R", "RW", "W", "R NATIVE", "RW NATIVE") ~ "Match",
        TRUE ~ "No match"
      )
  ) 
```


## Percentage questions answered

### Overall

On average, no-match respondents answer around 20% survey questions. There is a considerable number of participants answering less than 10% questions though.

```{r}
df_nomatch %>% 
  select(starts_with("q")) %>%
  na_if("No Data") %>% 
  mutate(
    row_nas = rowSums(!is.na(.)) / 20
  ) %>%
  ggplot(aes(row_nas)) +
  geom_histogram(fill = "gray", color = "black", binwidth = 0.05) +
  geom_vline(aes(xintercept = mean(row_nas, na.rm = TRUE)), linetype = "dashed", color = "blue") +
  scale_x_continuous(
    breaks = scales::breaks_width(0.1),
    labels = scales::percent_format(accuracy = 1)
  ) +
  theme_bw() +
  labs(
    x = "Percentage questions answered",
    y = "Number of respondents",
    caption = "Note: Blue dashed line represents the distribution mean"
  )
```


### By language proficiency

`match` highlights if the respondent was proficient in the followup survey language.

```{r}
df_nomatch %>% 
  select(starts_with("q"), lang_match) %>%
  na_if("No Data") %>% 
  mutate(
    row_nas = (rowSums(!is.na(.)) - 1)  / 20
  ) %>%
  ggplot(aes(row_nas)) +
  geom_histogram(fill = "gray", color = "black", binwidth = 0.05) +
  scale_x_continuous(
    breaks = scales::breaks_width(0.2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  facet_wrap(vars(lang_match)) +
  theme_bw() +
  labs(
    x = "Percentage questions answered",
    y = "Number of respondents"
  )
```


## No-match respondents anwering more than half questions

Around 20% no-match respondents (31 out of 188) answer more than half the survey questions. 

```{r}
df_nomatch %>% 
  select(starts_with("q")) %>% 
  na_if("No Data") %>% 
  mutate(
    row_nas = rowSums(!is.na(.)) / 20,
    answered_more_than_half = (row_nas >= 0.5)
  ) %>% 
  count(answered_more_than_half, name  = "count")
```


This rate is surprisingly higher among respondents without a language match.

```{r}
df_nomatch %>% 
  select(starts_with("q"), lang_match) %>% 
  na_if("No Data") %>% 
  mutate(
    row_nas = (rowSums(!is.na(.)) - 1)  / 20,
    answered_more_than_half = (row_nas >= 0.5)
  ) %>% 
  count(lang_match, answered_more_than_half, name  = "count")
```


## Question-wise response rate

### Overall

The response rate to questions falls as the survey proceeds.

```{r}
df_nomatch %>% 
  select(starts_with("q")) %>% 
  na_if("No Data") %>% 
  summarise_at(vars(starts_with("q")), ~ mean(!is.na(.))) %>% 
  pivot_longer(cols = starts_with("q"), names_to = "question", values_to = "answers") %>% 
  mutate(
    question = str_replace(question, "_nomatch", ""),
    question = str_replace(question, "q", "Question "),
    question = question %>% fct_inorder() %>% fct_rev()
    ) %>% 
  ggplot(aes(question, answers)) +
  geom_col(show.legend = FALSE) +
  scale_y_continuous(
    breaks = scales::breaks_width(0.1),
    labels = scales::percent_format(accuracy = 1)
  ) +
  theme_bw() +
  coord_flip() +
  labs(
    x = "Survey Questions",
    y = "Percentage respondents answering"
  )
```

### By language proficiency

The response rate falls more sharply for those with language matched after the first question. This could explain why they have lower percentage answering less than half the questions. 

The drop is relatively smoother for those with language mot matched.

```{r}
df_nomatch %>% 
  select(starts_with("q"), lang_match) %>% 
  na_if("No Data") %>% 
  group_by(lang_match) %>% 
  summarise_at(vars(starts_with("q")), ~ mean(!is.na(.))) %>% 
  pivot_longer(cols = starts_with("q"), names_to = "question", values_to = "answers") %>% 
  mutate(
    question = str_replace(question, "_nomatch", ""),
    question = str_replace(question, "q", "Question "),
    question = question %>% fct_inorder() %>% fct_rev()
    ) %>% 
  ggplot(aes(question, answers)) +
  geom_col(show.legend = FALSE) +
  scale_y_continuous(
    breaks = scales::breaks_width(0.2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  facet_wrap(vars(lang_match)) +
  theme_bw() +
  coord_flip() +
  labs(
    x = "Survey Questions",
    y = "Percentage respondents answering"
  )
```

