---
title: 'No-match data exploration'
#author: "Saurabh Khanna"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: 3
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE, fig.retina = 4)
knitr::opts_chunk$set(fig.pos = 'H')
```

```{r}
# Libraries
pacman::p_load(tidyverse, readxl, janitor, lubridate)

# Parameters
# df_baseline <- read_csv(here::here("data", "Rapid_response_baseline_20200904.csv"))
# df_updated <- read_xlsx(here::here("data", "merge/lirs_postresponses_updated_all_september.xlsx"))
df_nomatch <- read_xlsx(here::here("data", "merge/lirs_postresponses_nomatch_all_september.xlsx"))
# df_smslog <- read_csv(here::here("data", "merge/sms-log-jen-18sep2020.csv"))
```



```{r}
df_nomatch <-
  df_nomatch %>%
  mutate(date = as_datetime(date)) %>% 
  mutate_at(vars(starts_with("n")), parse_number) %>% 
  arrange(number, desc(date)) %>% 
  distinct(number, .keep_all = TRUE)
```


### Percentage questions answered

On average, no-match respondents answer around 20% survey questions. There is a considerable number of participants answering less than 10% questions though.

```{r}
df_nomatch %>% 
  select(starts_with("q")) %>%
  na_if("No Data") %>% 
  mutate(
    row_nas = rowSums(!is.na(.)) / 20
  ) %>%
  ggplot(aes(row_nas)) +
  geom_histogram(fill = "gray", color = "black", binwidth = 0.05) +
  geom_vline(aes(xintercept = mean(row_nas, na.rm = TRUE)), linetype = "dashed", color = "blue") +
  scale_x_continuous(
    breaks = scales::breaks_width(0.1),
    labels = scales::percent_format(accuracy = 1)
  ) +
  theme_bw() +
  labs(
    x = "Percentage questions answered",
    y = "Number of respondents",
    caption = "Note: Blue dashed line represents the distribution mean"
  )
```


### No-match respondents anwering more than half questions

Around 20% no-match respondents (31 out of 188) answer more than half the survey questions.

```{r}
df_nomatch %>% 
  select(starts_with("q")) %>% 
  na_if("No Data") %>% 
  mutate(
    row_nas = rowSums(!is.na(.)) / 20,
    answered_more_than_half = (row_nas >= 0.5)
  ) %>% 
  count(answered_more_than_half, name  = "count")
```


### Question-wise response rate

The response rate to questions falls as the survey proceeds. Question 4 is unique in a way that around 90% respondents don't answer it.


```{r}
df_nomatch %>% 
  select(starts_with("q")) %>% 
  na_if("No Data") %>% 
  summarise_at(vars(starts_with("q")), ~ mean(!is.na(.))) %>% 
  pivot_longer(cols = starts_with("q"), names_to = "question", values_to = "answers") %>% 
  mutate(
    question = str_replace(question, "_nomatch", ""),
    question = str_replace(question, "q", "Question "),
    question = question %>% fct_inorder() %>% fct_rev()
    ) %>% 
  ggplot(aes(question, answers)) +
  geom_col(aes(fill = (question != "Question 4")), show.legend = FALSE) +
  scale_y_continuous(
    breaks = scales::breaks_width(0.1),
    labels = scales::percent_format(accuracy = 1)
  ) +
  theme_bw() +
  coord_flip() +
  labs(
    x = "Survey Questions",
    y = "Percentage respondents answering"
  )
```

